Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-06-05 paper.tex
Add collapse profile and absorption sphere tests

\subsection{Homogenous Absorbing Star}
\label{ssec:test_ab_star}
[Test described in~\cite[Sec.~3.2]{smit1997-two_moment}.]
\todo{run test for optically thick and thin}

\subsection{Massive Collapsed Star with Scattering Envelope}
\label{ssec:test_scat_envelope}
[Standard radiation transport test described in~\cite{ocon2015-gr1d_with_nu},
and in \cite[App.~E.6]{fouc2015-m1_nsbh},
and in~\cite{abdi2012-monte_carlo}.]
\todo{add plots of $\langle \varepsilon \rangle(\mu)$}

@@

>>>>

\subsection{Homogenous Absorbing Star}
\label{ssec:test_ab_star}
[Test described in~\cite[Sec.~3.2]{smit1997-two_moment}.]
Plot in Fig.~\ref{fig:f_absorption_sphere}.

\subsection{Massive Collapsed Star with Scattering Envelope}
\label{ssec:test_collapse}
[Standard radiation transport test described in~\cite{ocon2015-gr1d_with_nu},
and in \cite[App.~E.6]{fouc2015-m1_nsbh},
and in~\cite{abdi2012-monte_carlo}.]
Plot in Fig.~\ref{fig:avg_eps_collapse}.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-absorption_sphere}
  \caption{Distribution function outside a constant-density star
    with radius $R=15$~km, and observer at $r=22.5$~km.
    $A$ is the angle between the neutrino momentum and the $\hat{r}$ direction.
    The sample grid uses 30 points in energy and angle spanning the ranges
    $\varepsilon\in(0,100)$~MeV and $\cos A\in(0.6454,1)$,
    with sample points at bin centers.
    The line depicts the analytic result for one energy: $\varepsilon=15$~MeV.
    Test described in Sec.~\ref{ssec:test_ab_star}}
  \label{fig:f_absorption_sphere}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{fig-collapse_profile-avg_eps_vs_cosA}
  \caption{Average energy $\langle\varepsilon\rangle=J/G$
    in the collapse profile test.
    The observer is at 500~km, and the shock at 150~km,
    so that the half-opening angle of the shock is $\cos A=0.954$.
    The four methods depicted are 1) a fiducial Monte Carlo calculation,
    ray tracing using the 2) spectral and 3) gray methods to estimate background
    fields for scattering, and 4) ray tracing neglecting scattering.
    Test described in Sec.~\ref{ssec:test_collapse}}
  \label{fig:avg_eps_collapse}
\end{figure}
